Air cargo load and route planning in pickup and delivery operations

### 2024-01-28 latex/eswa.tex
Main flow diagram

\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}

@@

@@

{\color{blue}
Scenario 6 will be used only for the best method validation.	
}

>>>>

\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes.arrows}

@@

% lets get the exact color
\usepackage{xcolor}
\definecolor{myblue}{HTML}{B0D7FF}

\tikzset{
	mybox/.style={rectangle,
		draw,
		fill= myblue,
		rounded corners,
		minimum width=2cm,
		inner sep=5pt,
		align=left,
		minimum height=1cm
	},
	myarrow/.style={draw=black,
		fill=white,
		minimum width=0.6cm,
		single arrow
	},
	longarrow/.style={draw=none,
		shading=axis,
		left color=white,
		right color=myblue,
		minimum width=0.6cm,
		single arrow,
		anchor=east
	}
}

@@

{\color{blue}
Scenario 6 will be used only for the best method validation.

Figure \ref{fig:flow} depicts the Algorithm \ref{alg:main} for easy understanding of the main flow.

\begin{figure}[htp]

	\centering
	\begin{tikzpicture}

		%% Make the boxes
		\node [mybox] (first)                        {Select:\\ 1. scenario\\2. surplus\\3. time limit};
		\node [mybox, right=0.7cm of first] (second) {Config:\\4. parameters\\5. cost matrix\\6. pallets\\7. items};
		\node [mybox, right=0.7cm of second] (third) {8. Define tour\\     schema:\\- All tours\\ \ \ \ (K-1)!\\ \ \ \ or\\- Solve a TSP\\ \ \ \ (set of tours))};
		\node [mybox, right=0.7cm of third] (fourth) {Solve ACLPP+RPDP:\\9. Many tours\\ \ \ \ (node-by-node)\\10. Select best tour};

		%% Draw arrows between them
		\node[myarrow] at ([xshift=8pt]first.east) {\phantom{\tiny{aaa}}};
		\node[myarrow] at ([xshift=8pt]second.east) {\phantom{\tiny{aaa}}};
		\node[myarrow] at ([xshift=8pt]third.east) {\phantom{\tiny{aaa}}};

	\end{tikzpicture} 
	\caption{Solution main flow}
	\label{fig:flow}
\end{figure}

### 2024-01-28 latex/responses.tex
Main flow diagram

@@

\paragraph{Revision:}
The inclusion of more figures to illustrate the flow, principle, and results of the algorithm would greatly enhance the clarity and visual representation.
\begin{center}
	\begin{minipage}{10cm}
		\textit{Agradecemos esta sugestão. Acrescentamos novas figuras e tabelas que ilustram melhor nossos resultados. Citar quais são...}
	\end{minipage}
\end{center}

>>>>

\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes.arrows}
% lets get the exact color
\usepackage{xcolor}
\definecolor{myblue}{HTML}{B0D7FF}

\tikzset{
	mybox/.style={rectangle,
		draw,
		fill= myblue,
		rounded corners,
		minimum width=2cm,
		inner sep=5pt,
		align=left,
		minimum height=1cm
	},
	myarrow/.style={draw=black,
		fill=white,
		minimum width=0.6cm,
		single arrow
	},
	longarrow/.style={draw=none,
		shading=axis,
		left color=white,
		right color=myblue,
		minimum width=0.6cm,
		single arrow,
		anchor=east
	}
}

@@

\paragraph{Revision:}
The inclusion of more figures to illustrate the flow, principle, and results of the algorithm would greatly enhance the clarity and visual representation.
\begin{center}
	\begin{minipage}{10cm}
		\textit{Agradecemos esta sugestão. Acrescentamos novas figuras e tabelas que ilustram melhor nossos resultados. Citar quais são...}

		{\color{blue}
		We included the figure below to depict the main algorithm for easy understanding of the main flow.
		}

		\begin{tikzpicture}

			\centering

		%% Make the boxes
\node [mybox] (first)                        {Select:\\ 1. scenario\\2. surplus\\3. time limit};
\node [mybox, right=0.7cm of first] (second) {Config:\\4. parameters\\5. cost matrix\\6. pallets\\7. items};
\node [mybox, right=0.7cm of second] (third) {8. Define tour\\     schema:\\- All tours\\ \ \ \ (K-1)!\\ \ \ \ or\\- Solve a TSP\\ \ \ \ (set of tours))};
\node [mybox, right=0.7cm of third] (fourth) {Solve ACLPP+RPDP:\\9. Many tours\\ \ \ \ (node-by-node)\\10. Select best tour};

%% Draw arrows between them
\node[myarrow] at ([xshift=8pt]first.east) {\phantom{\tiny{aaa}}};
\node[myarrow] at ([xshift=8pt]second.east) {\phantom{\tiny{aaa}}};
\node[myarrow] at ([xshift=8pt]third.east) {\phantom{\tiny{aaa}}};

		\end{tikzpicture}

		{\color{blue}
		We also included a map of Brazil with the 15 main busy airports and a tour for the reader to get an idea of how close to optimal the solution may be.
		}
